Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-12-22 SI.tex
resolve issues with paper and SI
Update to arXiv format

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,email=true,hyperref=true,keywords=false]{achemso}
%manuscript=suppinfo 
\usepackage{times}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage{braket}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

%\usepackage{xr}
\usepackage{xr-hyper} 
\externaldocument[main-]{paper_v120719}

\SectionNumbersOn{}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\theequation}{S\arabic{equation}}

@@

\title{Supplementary Information: \\ 
Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
\begin{document}

>>>>

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,email=true,hyperref=true,keywords=false,manuscript=suppinfo ]{achemso}
%manuscript=suppinfo 
\usepackage{times}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage{braket}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

%\usepackage{xr}
\usepackage{xr} 
\externaldocument[main-]{paper}

\SectionNumbersOn{}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\theequation}{S\arabic{equation}}
% \makeatletter
% \renewcommand\@biblabel[1]{S#1}
% \makeatother

@@

\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
\begin{document}
